Networked Character Devices

### 2011-12-11 report/paper.tex
Minro biblio chnages
Added images and advantages section

Devices which have been imported on the client reside within the
devtmpfs filesystem. This is almost always mounted on \texttt{/dev}. By
default an imported device will take on the name
\texttt{/dev/netchar/importN}, where \texttt{N} is the next available
number. In the future (and without much effort), imported devices will
be able to take on their original name from the server. For example, an
input device should be located at \texttt{/dev/input/eventN}. Furthermore,
the user or administrator may choose any mapping (s)he see fits.

@@

The protocol for NCD operates over TCP sockets. Despite the potential
for large amounts of streaming data over the internet --- data which may
be acceptable to drop --- some messages are unacceptable to lose. Any
request or reply should be guaranteed. The data following a
\texttt{read()} or \texttt{write()} (figure \ref{fig:protocol}), for
example, may not be as important. Therefore, in the future it may be
beneficial to implement the core protocol over TCP and bulk data over
UDP (section \ref{sec:futurework}).

@@

@@

>>>>

Devices which have been imported on the client reside within the
devtmpfs file system. This is almost always mounted on \texttt{/dev}. By
default an imported device will take on the name
\texttt{/dev/netchar/importN}, where \texttt{N} is the next available
number. In the future (and without much effort), imported devices will
be able to take on their original name from the server. For example, an
input device should be located at \texttt{/dev/input/eventN}. Furthermore,
the user or administrator may choose any mapping (s)he see fits.

@@

The protocol for NCD operates over TCP sockets. Despite the potential
for large amounts of streaming data over the Internet --- data which may
be acceptable to drop --- some messages are unacceptable to lose. Any
request or reply should be guaranteed. The data following a
\texttt{read()} or \texttt{write()} (figure \ref{fig:protocol}), for
example, may not be as important. Therefore, in the future it may be
beneficial to implement the core protocol over TCP and bulk data over
UDP (section \ref{sec:futurework}).

@@

The primary advantages of using Networked Charterer Devices are:

\begin{packed_item}
\item Divorces peripherals from the computers to which they are
  attached
\item Allows simple creation of a ``Device Server''
\item Extends the ``Everything Is A File'' -nix philosophy
\item Allows more efficient use of devices
\item Allows devices to be networked in a generalized, uniform manner
\end{packed_item}

By allowing the interface for any device to be exported over the
network, the NCD system effectively removes the traditional restriction
that devices are only available on the hosts to which they are
physically connected. Removing this restriction has far reaching
implications (see Section \ref{sec:potentialuses}). One of which is
increased efficiency of device utilization. By allowing devices to
be exported from machines where they are not needed and imported on
machines where they are, we can insure that devices are efficiently
utilized without having to worry about the underlying physical locations
of the devices.

One of the foremost tenants of the Unix philosophy is the ``Everything
is a file'' concept. The NCD system extends this concept to
``Everything is a networked file''. This allows us to create ``Device
Servers'' as easily as we currently create file servers. The NCD
system allows us to network any device via the general and
well-understood file interface instead of relying on devices specific
networking implementations.

@@

\section{Potential Uses}
\label{sec:potentialuses}

\subsection{Networked KVM System}
\label{sec:networkedkvm}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{kvm-g.png}
  \caption{A networked KVM system built using NCD.}
  \label{fig:kvm}
\end{figure}

\subsection{Distributed RNG System}
\label{sec:distributedrng}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{rng-g.png}
  \caption{A distributed Random Number Generator system built using NCD.}
  \label{fig:rng}
\end{figure}
